---
title: "Final_Presentation1"
author: "SAMIKSHA VENUGOPAL"
date: "12/8/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
```{r}
###  Install required packages 
library(readr)
library(dplyr)
library(arules)
library(arulesViz)
library(plyr)
library(ggplot2)

```


##     Cross marketing

## The technique used to solve and infer the issue using association rules. 

## Loading the file into R 

## The data set contain the  contains purchase data from April 2020 to November 2020 from a large home appliances and electronics online store. 

## Reading the file as Kz

```{r}
### Reading the file
getwd()
setwd("/users/Samikshachalla/downloads")
kz<-read.csv("kz.csv")
head(kz)
```

`
## Data Prepartion for prediction
## set the seed for the radom number generator for predictability
```{r}
## Re-viewing the dataset

set.seed(111)
str(kz)
summary(kz)

```


## Considering order ID

```{r}
## Clearning the data 

## Removing single items order

order_freq<-table(kz$order_id)
hist(order_freq)


```
## Items brought in each order is in range of r range ( order_fre)
```{r}

order_freq<-order_freq[order_freq>1]
kz<-subset(kz,kz$order_id%in% names(order_freq),c("order_id","category_code"))


```

## Removing duplicate items from order list


```{r}

rm(order_freq)
kz<-unique(kz)

```

## Convert the data frame into basket format
```{r}



  if(sessionInfo()['basePkgs']=="dplyr" | sessionInfo()['otherPkgs']=="dplyr"){
  detach(package:dplyr, unload=TRUE)
  }

 df_itemList <- ddply(kz,c("order_id"),
                      function(kz)paste(kz$category_code,
                      collapse = ","))

rm(kz)
df_itemList$order_id <- NULL


```

## Rename column header for ease of use


```{r}


colnames(df_itemList) <- c("itemList")
write.csv(df_itemList,"ItemList.csv",row.names = TRUE)
rm(df_itemList)

```

# Compute transactions for the product names from the order baskets

```{r}
# Find the association rules

txn = read.transactions(file="ItemList.csv", rm.duplicates= TRUE, format="basket",sep=",",cols=1);
txn@itemInfo$labels <- gsub("\"","",txn@itemInfo$labels)
basket_rules <- apriori(txn,parameter = list(sup = 0.001, conf = 0.001,target="rules"))
basket_rules

summary(basket_rules)
```
## plot

```{r}

## Plot basket rules

itemFrequencyPlot(txn,topN=20,type="absolute",col=cm.colors(20), main="Absolute Item Frequency Plot")
plot(basket_rules)
plot(basket_rules, method="graph", control=list(type="items"))


```
##Find the association rules with sup = 0.005
```{r}
# Find the association rules with sup = 0.005
txn = read.transactions(file="ItemList.csv", rm.duplicates= TRUE, format="basket",sep=",",cols=1);
txn@itemInfo$labels <- gsub("\"","",txn@itemInfo$labels)
basket_rules <- apriori(txn,parameter = list(sup = 0.005, conf = 0.01,target="rules"))
basket_rules

summary(basket_rules)



```
##Plot
```{r}
## Plot basket rules


itemFrequencyPlot(txn,topN=20,type="absolute",col=cm.colors(20), main="Absolute Item Frequency Plot")
plot(basket_rules)
plot(basket_rules, method="graph", control=list(type="items"))
```
## Camparing the results with between sup = 0.001 and sup = 0.005
```{r}
## Find the association rule with conf= 0.001
txn = read.transactions(file="ItemList.csv", rm.duplicates= TRUE, format="basket",sep=",",cols=1);
txn@itemInfo$labels <- gsub("\"","",txn@itemInfo$labels)
basket_rules <- apriori(txn,parameter = list(sup = 0.001, conf = 0.001,target="rules"))
basket_rules

summary(basket_rules)


```

```{r}
itemFrequencyPlot(txn,topN=20,type="absolute",col=cm.colors(20), main="Absolute Item Frequency Plot")
plot(basket_rules)
plot(basket_rules, method="graph", control=list(type="items"))

```
## Inspect

```{r}
## Association rules for departments in orders dataset
basket_rules <- apriori(txn, parameter = list(supp = 0.001, conf = 0.001))
summary(basket_rules)
rules1d_order_conf <- sort(basket_rules, by="conf", decreasing = TRUE)
inspect(head(rules1d_order_conf, 10))
rules1d_order_lift <- sort(basket_rules, by="lift", decreasing = TRUE)
inspect(head(rules1d_order_lift, 10))
basket_rules2 <- apriori(txn, parameter = list(supp = 0.005, conf = 0.01))
summary(basket_rules2)
rules2d_order_conf <- sort(basket_rules2, by="conf", decreasing = TRUE)
inspect(head(rules2d_order_conf, 10))
rules2d_order_lift <- sort(basket_rules2, by="lift", decreasing = TRUE)
inspect(head(rules2d_order_lift, 10))

 

```

 ## Top 5 
```{r}
 library(arulesViz)
 top5rules <- (basket_rules[1:5])
 plot(top5rules, method = "graph")
 
```
## Top 10
```{r}
library(arulesViz)
 top5rules <- (basket_rules[1:10])
 plot(top5rules, method = "graph")
 
```


```{r}

plot(basket_rules2)

```
```{r}
head(quality(basket_rules2))
```


```{r}
plot(basket_rules2,measure = c("support","lift"),shading = "confidence")
```

```{r}
plot(basket_rules2,method = "two-key plot")

```
##Matrix based visulization
```{r}
subrules <- basket_rules2[quality(basket_rules2)$confidence > 0.5]
subrules

```

## Double Decker plot
```{r}

oneRule <- sample(basket_rules,1)
inspect(oneRule)
 
 
```
```{r}
plot(oneRule,data = kz)
```





